---
title: "HW5"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, state), resolution = case_when(
    disposition == "Closed without arrest" ~ "unsolved", 
    disposition == "Open/No arrest" ~ "unsolved", 
    disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Focusing on Baltimore, MD: 

```{r}
baltimiore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimiore_df %>% 
  summarize(unsolved = sum(resolution == "unsolved"), 
            n = n())

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved), 
    n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's get those estimates across all cities 

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
  city_df %>% 
  summarize(unsolved = sum(resolution == "unsolved"), 
            n = n())

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved), 
      n = city_summary %>% pull(n))

  return(city_test)
  
}

prop_test_function(baltimiore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Plot estimates and confidence intervals 

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Other approach: 

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

```{r}
tibble(
  list.files("data/data/"))
```


each data set is a subject with 

use something like a function to iterate across ecah of these to read_csv across each file; then, you end up with a dataset with a column of data; then unnest and have all the columns that i need to have; 

then you need to tidy that result (get a control arm and an experimental arm, its in wide format instead of long format, you need a unique ID, then you get a dataset that you can use to create a spaghetti plot)

## Problem 3 
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function 

```{r}
fill_in_missing = function(vector) {
  
  if (is.numeric) {
    
    
  }
  
  if(is.character) {
    
    
  }
  
  
}
```
 if neither of those things, then spit out a warning message; 
 
 then if you have this written, I would check that it fills in the way that it needs to
 
 Where the mapping piece comes in, I would start at the first column and map across each of the columns and update each of the columns within the dataframe and then put it back together as a dataframe 





