---
title: "HW5"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r, message = FALSE}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(city_state = str_c(city, state), resolution = case_when(
    disposition == "Closed without arrest" ~ "unsolved", 
    disposition == "Open/No arrest" ~ "unsolved", 
    disposition == "Closed by arrest" ~ "solved")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Focusing on Baltimore, MD: 

```{r, message = FALSE}
baltimiore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimiore_df %>% 
  summarize(unsolved = sum(resolution == "unsolved"), 
            n = n())

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved), 
    n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Getting the estimates across all cities 

```{r, message = FALSE}
prop_test_function = function(city_df) {
  
  city_summary = 
  city_df %>% 
  summarize(unsolved = sum(resolution == "unsolved"), 
            n = n())

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved), 
      n = city_summary %>% pull(n))

  return(city_test)
  
}

prop_test_function(baltimiore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

```{r, message = FALSE}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Plot estimates and confidence intervals 

```{r, message = FALSE}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Other approach from office hours for reference: 

```{r, message = FALSE}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"), 
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

```{r, message = FALSE, warning=FALSE}
importcsv = function(filename) {
  
  x = str_c("data/data/", filename)
  data = read_csv(x)
  
  return(data)
}

importcsv("con_01.csv")

prob2_df = 
  tibble(
  name = list.files("data/data/"), 
  data = map(name, importcsv))

full_data_2 = 
  prob2_df %>% 
    separate(name, c("treatment_arm", "id")) %>% 
  mutate(id = as.numeric(id), 
         treatment_arm = as.factor(treatment_arm)) %>% 
    unnest(data) %>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week", 
    names_prefix = "week_"
  ) %>% 
  mutate(id = ifelse(treatment_arm == "exp", id, id+10))

full_data_2 %>% 
  ggplot(aes(x = week, y = value, group = id, color = treatment_arm)) +
  geom_line() +
  labs(x = "Week", y = "Value") + 
  scale_color_discrete(name = "Trial Arm", labels = c("Control", "Experimental"))
```

Based on the spaghetti pot, it appears that those in the experimental arm tend to have higher values than those in the control arm by the end of week 8; however, values appeared much closer together at the beginning of the trial period (meaning week 1). If the goal of the treatment was to increase the values, it appears that the treatment was effective. 

## Problem 3 
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Function to fill in missing: 

```{r}
fill_missing = function(x) {
  
  if(is.character(x)) {
    
    x[is.na(x)] = "virginica"
  
    }
  
  if(is.numeric(x)) {
    
    x[is.na(x)] = mean(x, na.rm = TRUE)
    
  }
  
    if(!is.character(x) & !is.numeric(x)){
    stop("vector is not numeric or character")
  }
  
  
  return(x)
  
}

fill_missing(iris_with_missing$Sepal.Length)
fill_missing(iris_with_missing$Sepal.Width)
fill_missing(iris_with_missing$Petal.Length)
fill_missing(iris_with_missing$Petal.Width)
fill_missing(iris_with_missing$Species)

iris_filled = 
  iris_with_missing %>% 
  map_df(fill_missing) 

sum(is.na(iris_with_missing$Sepal.Length))
sum(is.na(iris_filled$Sepal.Length))

sum(is.na(iris_with_missing$Sepal.Width))
sum(is.na(iris_filled$Sepal.Width))

sum(is.na(iris_with_missing$Petal.Length))
sum(is.na(iris_filled$Petal.Length))

sum(is.na(iris_with_missing$Petal.Width))
sum(is.na(iris_filled$Petal.Width))

sum(is.na(iris_with_missing$Species))
sum(is.na(iris_filled$Species))

```






